# Downloading arrests for your area

```{r}
#| label: get-aor-state-lists
#| include: true
#| echo: false
#| message: false
#| warning: false
#| error: true
#| eval: true

library(tidyverse)
library(here)
library(reactable)
library(reactablefmtr)
i_am("recipes-arrest-download.qmd")

aor_index <- read_csv("data/aor_csv_summary.csv")
state_index <- read_csv("data/state_csv_summary.csv")



```


BLN is providing data files for ICE arrests in two ways: By state and by ICE's Area of Responsibility. In some areas, this AOR is a portion of a state. In others, it covers many states.




## State files

We expect most reporters will work with files for their state or a few neighboring states. There are two exceptions:

1. Some states have too many rows for you to handle efficiently -- more on this below, but we recommend against using Google Sheets for any of these datasets with more than about 15,000 rows. It may be easier to work with Area of Responsibility files instead.

2. In other cases, the area of responsibility gets you closer to your local area, such as the Washington, D.C. and Virginia area, or the area around New York City.

```{r}
#| label: state-table
#| include: true
#| echo: false
#| warning: false
#| message: false
#| eval: true


google_bucket <- "https://data.biglocalnews.org/deportation-data/arrests/"

# example url
#https://data.biglocalnews.org/deportation-data/arrests/ak_ice_arrests.csv

state_index |>
  select ( state_name, row_count, file_name) |>
  reactable (
    searchable=TRUE,
    wrap = TRUE,
    striped=TRUE,
    sortable=TRUE,
    filterable=TRUE,
    defaultPageSize = 10,
    columns = list (
      state_name = colDef(name="State",
                        cell=function (value, index) {
                          url <- paste0(google_bucket, state_index[index, "file_name"])
                          htmltools::tags$a(href=url, value)
                          }
                        ),
      file_name  = colDef( show=FALSE) ,
      row_count = colDef(name = "# rows", format=colFormat(separators = TRUE, digits=0) )
    )
  )



```



## Area of Responsibility files

There is some inconsistency in the data included for ICE's area of responsibility. In some instances, like Arizona, there are substantially more rows in the state records than the area of responsibility because the AOR was missing in so many rows. But for large areas, this may be the most effective ways of working with your counties.


```{r}
#| label: aor-table
#| include: true
#| echo: false
#| warning: false
#| message: false
#| eval: true

google_bucket <- "https://data.biglocalnews.org/deportation-data/arrests/"

# example url
#https://data.biglocalnews.org/deportation-data/arrests/ak_ice_arrests.csv


aor_index |>
  select ( aor_name, states, row_count, file_name) |>
  reactable (
    searchable=TRUE,
    wrap = TRUE,
    striped=TRUE,
    sortable=TRUE,
    filterable=TRUE,
    defaultPageSize = 10,
    columns = list (
      aor_name = colDef(name="Area of Responsibility",
                        cell=function (value, index) {
                          url <- paste0(google_bucket, aor_index[index, "file_name"])
                          htmltools::tags$a(href=url, value)
                          }
                        ),
      states = colDef(name = "States"),
      file_name  = colDef( show=FALSE) ,
      row_count = colDef(name = "# rows", format=colFormat(separators = TRUE, digits=0) )
    )
  )



```


## Working with large files

Google sheets has a technical limit of 10 million individual cells, but in practice it starts crashing with more than about 15,000 rows of this dataset, which has 31 columns. If your area has more rows than this, consider switching to Microsoft Excel, with its larger capacity.

The two highest-volume areas will be particularly difficult to handle in Google Sheets: Florida and the Dallas AOR.

If you are working with a very large file, look for ways to reduce the size right after you import it into Google Sheets. For example, the list of arrests for Texas is too large for the program, but even the Dallas Area of Resposibility is quite large -- about 30,000 rows. You can reduce this size a little by deleting any rows not in Texas. (Note that my Google Sheet crashed a couple of times trying to delete these rows. )

Contact BLN to help you reduce the size of your spreadsheet if you need help -- we may be able to find a strategy that will work for your story or provide you with a pre-filtered list.
